### 2020-10-07 priority-cp.tex
on operational semantics

\subsection{Typing}
Typing rules for our version of PCP are given in \cref{fig:pcp-typing}. A typing judgement $\seq{P}{\Gamma}$ states that "process $\tm P$ is well typed under the typing context $\ty \Gamma$".

@@

\input{fig/pcp-typing}

\subsection{Operational Semantics}
See \cref{fig:pcp-operational-semantics}.
\input{fig/pcp-operational-semantics}

@@

\begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
  \label{lem:pcp-canonical-forms}
  If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
\end{restatablelemma}
\begin{proof}
  If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
\end{proof}
\todo{We need to comment here why it is that we presented canonical forms, to start with...}
\begin{restatabletheorem}{thmpcpclosedprogress}[Closed Progress, $\red$]
  \label{thm:pcp-closed-progress}
  \hfill\\%newline before theorem statement
  If $\seq{P}{\emptyenv}$ and $\tm{P}$ is in canonical form, then either $\tm{P}=\tm{\halt}$ or there exists a $\tm{Q}$ such that $\tm{P}\red\tm{Q}$.
\end{restatabletheorem}
\begin{proof}
  Details in~\cref{prf:thm-pcp-closed-progress}.
\end{proof}

>>>>

\subsection{Typing}
\input{fig/pcp-typing}

Typing rules for our version of PCP are given in \Cref{fig:pcp-typing}. A typing judgement $\seq{P}{\Gamma}$ states that "process $\tm P$ is well typed under the typing context $\ty \Gamma$".

@@

\subsection{Operational Semantics}
\input{fig/pcp-operational-semantics}

The operational semantics for PCP given in \Cref{fig:pcp-operational-semantics} is defined as a reduction relation $\red$ on processes (bottom) and uses structural congruence (top).

Structural congruence satisfies the following axioms. $\LabTirName{SC-LinkSwap}$ allows swapping channels in the link process. $\LabTirName{SC-ResLink}$ allows restriction to applied to link which is structurally equivalent to the terminated process, thus allowing elimination of unnecessary restrictions. $\LabTirName{SC-ResSwap}$ allows swapping channels and $\LabTirName{SC-ResComm}$ states that restriction is commutative. $\LabTirName{SC-ResExt}$ is the standard scope extrusion rule. Rules $\LabTirName{SC-ParNil}$, $\LabTirName{SC-ParComm}$ and $\LabTirName{SC-ParAssoc}$ state that parallel composition uses the terminated proceess as the neutral element; it is commutative and associative.

The reduction relation is given by a set of axioms and inference rules for context closure. Reduction occurs under restriction following \cite{dardha2018} where channel endpoints are identified.
$\LabTirName{E-Link}$ reduces a parallel composition with a link into a substitution. $\LabTirName{E-Send}$ is the main communication rule, where send and receive processes sychronise and reduce to the corresponding continuations. $\LabTirName{E-Close}$ follows the previous rule and it closes the channel identified by endpoints $\tm x$ and $\tm y$. $\LabTirName{E-Select-Inl}$ and $\LabTirName{E-Select-Inr}$ are generalised versions of $\LabTirName{E-Send}$. They state respectively that a left and right selection synchronises with a choice offering and reduces to the corresponding continuations. The last three rules state that reduction is closed under restriction, parallel composition and structural congruence, respectively.

@@

\begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
  \label{lem:pcp-canonical-forms}
  If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
\end{restatablelemma}
\begin{proof}
  If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
\end{proof}
\todo{We need to comment here why it is that we presented canonical forms, to start with...}
\begin{restatabletheorem}{thmpcpclosedprogress}[Closed Progress, $\red$]
  \label{thm:pcp-closed-progress}
  \hfill\\%newline before theorem statement
  If $\seq{P}{\emptyenv}$ and $\tm{P}$ is in canonical form, then either $\tm{P}=\tm{\halt}$ or there exists a $\tm{Q}$ such that $\tm{P}\red\tm{Q}$.
\end{restatabletheorem}
\begin{proof}
  Details in~\Cref{prf:thm-pcp-closed-progress}.
\end{proof}
